HAMdetector: A Bayesian regression model that integrates information to detect HLA-associated mutations

### 2021-02-16 docs/main.tex

The logit transform is used because it cancels out with the logistic inverse link function. This means that the phylogeny information acts as a baseline in absence of any HLA effects. As this baseline itself is not certain but subject to errors of the phylogenetic probabilities $P(y_{ik}=1|\Psi)$, we introduce an additional parameter $\gamma_k$, constrained to be positive.
\hl{DaHo: Please check prior for $\gamma_k$. Constraint ok?}

@@

\begin{itemize}
  \item A large HIV dataset consisting of 1383 sequences, that were kindly provided by Zabrina Brumme and collaborators and were also used in the Phylogenetic Dependency Network study~\citep{Carlson2008}.
  \item A set of 351 HIV sequences mostly spanning the Pol gene from the Arevir database~\citep{Roomp2006}.
  \item A set of 544 Hepatitis-B-Virus sequences that were kindly provided by Jörg Timm.
  \item A set of 104 Hepatitis-D-Virus sequences that were kindly provided by Michael Roggendorf. \hl{DaHo: bitte von Hadi geeignetes Zitat erfragen}
  \item A set of 41 HIV sequences that were kindly provided by Rongge Yang. 
\end{itemize}

\hl{DaHo: zu jedem Datensatz die Proteine nennen}

>>>>

The logit transform is used because it cancels out with the logistic inverse link function. The phylogeny term acts as a baseline in absence of any HLA effects. As this baseline itself is not certain but subject to errors of the phylogenetic probabilities $P(y_{ik}=1|\Psi)$, we introduce an additional parameter $\gamma_k$.

@@

\begin{itemize}
  \item A large HIV dataset consisting of 1383 sequences, that were kindly provided by Zabrina Brumme and collaborators and were also used in the Phylogenetic Dependency Network study~\citep{Carlson2008}. The dataset contains sequences spanning the \textit{gag}, \textit{pol}, \textit{env}, \textit{nef}, \textit{vif}, \textit{vpr}, \textit{vpu}, \textit{tat} and \textit{rev} genes.
  \item A set of 351 HIV sequences mostly spanning the \textit{pol} gene from the Arevir database~\citep{Roomp2006}.
  \item A set of 544 Hepatitis-B-Virus sequences that were kindly provided by Jörg Timm. The dataset contains sequences of the HBe, LHBs, Pol and HBx proteins.
  \item A set of 104 Hepatitis-D-Virus sequences containing the HDV-antigen that were kindly provided by Michael Roggendorf. \hl{DaHo: bitte von Hadi geeignetes Zitat erfragen}
  \item A set of 41 HIV sequences spanning the \textit{gag} and \textit{pol} genes that were kindly provided by Rongge Yang. 
\end{itemize}
